Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area.

### 2022-06-13 outputs/paper/paper.qmd
Update paper.qmd

---
title: "paper.qmd"
author: "Sarah Mansoor"
format: pdf
editor: visual
---

## Quarto

Quarto enables you to weave together content and executable code into a finished document. To learn more about Quarto see <https://quarto.org>.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

>>>>

---
title: "Disparities in Climate-Induced Health Outcomes in the Greater Toronto Area."
author: "Sarah Mansoor"
thanks: "Code and data are available at: https://github.com/sarahmansoorr/SUDS2022"
date: "`r format(Sys.time(), '%d %B %Y')`"
format: pdf
editor: visual
bstract: ""
---

## Introduction

## Data

## Visualizing the Data and the Implications

## Next Steps
